Large-scale harmonic patterns clustering

### 2010-03-10 Paper/Paper.tex
improved

\begin{algorithm}
%\caption{Pseudocode of Vector Quantization}
\label{algo:vq}
\begin{algorithmic}
\STATE$l$ learning rate
\STATE$\{P_n\}$ set of patches
\STATE$\{C_k\}$ codebook of $K$ codes
%\STATE $m \leftarrow b$
\REQUIRE $0 < l \leq 1$
\FOR{$nIters$}
\FOR{$p \in \{P_n\}$}
\STATE$c \leftarrow min_{c \in C_k} dist(p,c)$
\STATE$c \leftarrow c + (p - c) * l$
\ENDFOR
\ENDFOR
\RETURN $\{C_k\}$
\caption{{Pseudocode of Online Vector Quantization. Note that we can replace
the number of iteration by a threshold on the distortion over some test set.}}
\end{algorithmic}
\end{algorithm}

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|l|c|}
\hline
\# codes & \# samples & avg. dist \\ \hline \hline
1 & $500$ & $0.195939$ \\
10 & $5$K & $0.161812$ \\
50 & $25$K & $0.147472$ \\
100 & $50$K & $0.142194$ \\
200 & $100$K & $0.137548$ \\
500 & $250$K & $0.131211$ \\
1000 & $500$K & \\ \hline
\end{tabular}
\end{center}
\caption{{Code book size.}}
\label{tab:cbsize}
\end{table}
% RESULTS:      avg_distsOLD    avg_dist
% code 1        0.195939
% code 10       0.161812
% code 50       0.147472
% code 100      0.142194
% code 200      0.137548
% code 500      0.131211

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|}
\hline
\# codes & \# bars & avg. dist \\ \hline \hline
2 & $1$ & $0.058435$ \\
4 & $2$ & $0.054792$ \\
16 & $4$ & $0.055489$ \\
256 & $8$ & $0.054860$ \\ \hline
2 & $2$ beats & $0.046955$ \\
4 & $1$ & $0.$ \\
16 & $2$ & $0.$ \\
256 & $4$ & $0.$ \\ \hline
\end{tabular}
\end{center}
\caption{{Code book size in function of the number of bars to encode.
All experiments done wtih $256 \times 500 = 128$K samples randomly chosen.}}
\label{tab:size_pattern}
\end{table}
% RESULTS:           avg_distsOLD   avg_dist
%2 codes 1 bar       0.180750       0.058435
%4 codes 2 bars      0.183631       0.054792
%16 codes 4 bars     0.184078       0.055489
%256 codes 8 bars    0.183464       0.054860
%---------------
%2 codes 2 beats     0.166840       0.046955
%4 codes 1 bar       0.171495       0
%16 codes 2 bars     0.173767
%256 codes 4 bars    0.174169       0

@@

Note that NMF does not solve the same problem. It tries to explain each pattern
as a combination of codes. Thus it does not perform clustering, though you
could cluster patterns using their encoding weights.

@@

>>>>

\begin{algorithm}
%\caption{Pseudocode of Vector Quantization}
\begin{algorithmic}
\STATE$l$ learning rate
\STATE$\{P_n\}$ set of patches
\STATE$\{C_k\}$ codebook of $K$ codes
%\STATE $m \leftarrow b$
\REQUIRE $0 < l \leq 1$
\FOR{$nIters$}
\FOR{$p \in \{P_n\}$}
\STATE$c \leftarrow min_{c \in C_k} dist(p,c)$
\STATE$c \leftarrow c + (p - c) * l$
\ENDFOR
\ENDFOR
\RETURN $\{C_k\}$
\caption{{Pseudocode of Online Vector Quantization. Note that we can replace
the number of iteration by a threshold on the distortion over some test set.}
\label{algo:vq}}
\end{algorithmic}
\end{algorithm}

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|l|c|}
\hline
\# codes & \# samples & avg. dist \\ \hline \hline
1 & $500$ & $0.195939$ \\
10 & $5$K & $0.161812$ \\
50 & $25$K & $0.147472$ \\
100 & $50$K & $0.142194$ \\
200 & $100$K & $0.137548$ \\
500 & $250$K & $0.131211$ \\
1000 & $500$K & \\ \hline
\end{tabular}
\end{center}
\caption{{Code book size.}}
\label{tab:cbsize}
\end{table}
% RESULTS:      avg_distsOLD    avg_dist
% code 1        0.195939        0.066079
% code 10       0.161812        0.045690
% code 50       0.147472        0.038456
% code 100      0.142194        0.036725
% code 200      0.137548        0.
% code 500      0.131211        0.

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|}
\hline
\# codes & \# bars & avg. dist \\ \hline \hline
2 & $1$ & $0.058435$ \\
4 & $2$ & $0.054792$ \\
16 & $4$ & $0.055489$ \\
256 & $8$ & $0.054860$ \\ \hline
2 & $2$ beats* & $0.066416$ \\
4 & $1$ & $0.050712$ \\
16 & $2$ & $0.050172$ \\
256 & $4$ & $0.04989$ \\ \hline
\end{tabular}
\end{center}
\caption{{Code book size in function of the number of bars to encode.
All experiments done wtih $256 \times 500 = 128$K samples randomly chosen.
* For the $2$ beats experiment, we take the first half of every beats.
It is different from ignoring bars and taking every $2$ beats. It is more
coherent with the other settings ($1-2-4-8$ bars).}}
\label{tab:size_pattern}
\end{table}
% RESULTS:           avg_distsOLD   avg_dist
%2 codes 1 bar       0.180750       0.058435
%4 codes 2 bars      0.183631       0.054792
%16 codes 4 bars     0.184078       0.055489
%256 codes 8 bars    0.183464       0.054860
%---------------
%2 codes 2 beats     0.166840       0.046955
%2 codes 2 beats                    0.066416
% based on bars
%4 codes 1 bar       0.171495       0.050712
%16 codes 2 bars     0.173767       0.050172
%256 codes 4 bars    0.174169       0.049894

@@

Note that NMF does not solve the same problem. It tries to explain each pattern
as a combination of codes. Thus it does not perform clustering, though you
could cluster patterns using their encoding weights. Also, we do not fully
compare our methods with NMF, it would be a paper on its own.

@@

\subsection{Experiment}
Put figure, compare basis, yeah!
